Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-08-05 sections/3algebras.tex
Minor changes.

\begin{remark}
    Let's unwind the above definition to understand the underlying data needed to define a prefactorization algebra. On the level of objects, for every open set $U$ we need to assign an object $F(U) \in \catC$. On the level of morphisms, given a pairwise disjoint set of opens $\{U_i\}_{i \in I}$ and an open $U$, such that the $U_i$ all lie in $U$ we need to assign a morphism in $\catC$
    %
    \begin{equation}
        \bigotimes_{i \in I} F(U_i) \xrightarrow{F(\{U_i\},U)} F(U).
    \end{equation}
    %
    As the notation suggests and the operadic symmetry condition guarantees, the maps $F(\{U_i\},U)$ only depend on the set of $U_i$ and not on any particular order of the $U_i$, which is also allowed on the left-hand side by the symmetric monoidal structure of $\catC$. Furthermore, the operadic associativity condition imposes that given pairwise disjoint $\{U_i\}_{i \in I}$ that all lie in $U$, and for each $i \in I$, pairwise disjoint $\{ V_{i, j}\}_{j \in J_i}$ that all lie in $U_i$, there is a commutative diagram in $\catC$
    %
    \begin{equation}
        \begin{tikzcd}
            \bigotimes\limits_{(i,j)} F(V_{i,j}) \arrow[rd, shorten <=-2ex, "\bigotimes\limits_{i} F(\{V_{i, j}\} {,} U_i)"'] \arrow[rr, "F( \{V_{i, j}\} {,} U)"] &   & F(U) \\
            & \bigotimes\limits_{i} F(U_i) \arrow[ru, "F( \{U_i \} {,} U)"'] &,          
        \end{tikzcd}
    \end{equation}
    %
    where the $(i,j)$ tensor product runs over all possible pairs $i \in I$ and $j \in J_i$. Finally, the operadic unitarity condition actually tells us that the morphisms $F(\{U\}, U)$ are equivalent to the identity morphism.

@@

    Given a Weiss cover $\mathscr{U}$ on $N$ we can restrict it to a Weiss cover $\mathscr{U}_{[B]}$ of $N_{[B]}$ by intersecting. The statement of \Cref{lem:weiss_to_ordinary} is that we can build an ordinary cover $\mathscr{U}_{i_{[B]},[B]}$ of $\mathrm{UConf}_{i_{[B]}}(N_{[B]})$. $\mathscr{V}_{\iota}^{[B]}$ is a cover if for any $p \in \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(N)$ we can find an open $\widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U)$ that contains it. But this is indeed the case, because looking at the target $t(p)$ of the path $p$, we get $t(p) \in \mathrm{UConf}_{i_{[B]}}(N_{[B]})$, and we know that there exists a $U \in \mathscr{U}$ such that $\mathrm{UConf}_{i_{[B]}}(U_{[B]})$ covers $t(p)$ and subsequently also that $\widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U)$ covers $p$.

    ...
\end{proof}

@@

\begin{proof}[Proof of {\Cref{thm:disk_alg=lcfa}}]
    To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later. Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding an equivalence of prefactorization algebras, namely a family of equivalences
    %
    \begin{equation}
        \int_U F| \xrightarrow[\simeq]{\ \ \phi (U) \ \ } F(U),
    \end{equation}
    %
    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which are natural in $U$ and preserve the multiplicative structure (see \Cref{cd:fa_morphisms}). Since $F$ is a locally constant factorization algebra the functor
    %
    \begin{equation}
        \lcfa_M (\catC) \xrightarrow{} \csheaves[W, lc](\mfld[r]_{/M}, \catC) \simeq \csheaves[W](\mfld_{/M}, \catC) \xrightarrow{} \mathsf{Fun}(\mfld_{/M}, \catC),
    \end{equation}
    %
    which we omit in the notation, allows us to consider $F$ as a functor from $\mfld_{/M}$. Furthermore, since $\disk[r]_{/U}$ is a Weiss sieve we can write
    %
    \begin{align}
        F(U) &\simeq \mathsf{colim} (\disk[r]_{/U} \xrightarrow{} \disk[r]_{/M} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{F} \catC).
    \end{align}
    %
    By consulting the commutative diagram
    % 
    \begin{equation}
        \begin{tikzcd}
            \disk[r]_{/U} \arrow[d] \arrow[r] & \disk_{/U} \arrow[d] & \\
            \disk[r]_{/M} \arrow[d] \arrow[r] & \disk_{/M} \arrow[d] \arrow[r, "F|"] & \catC, \\
            \mfld[r]_{/M} \arrow[r] & \mfld_{/M} \arrow[ru, "F"'] &  
        \end{tikzcd}
    \end{equation}
    %
    where $F|$ is the restriction of $F$ to disks, and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
    %
    \begin{equation}
        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) \simeq \int_U F|.
    \end{equation}
    %
    Naturality of these equivalences is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$. Given this fact, to preserve the multiplicative structure it is enough to show that the following is a commutative diagram
    %
    \begin{equation}\label{eq:mult_strut_comm_square}
        \begin{tikzcd}
            \otimes_i \int_{U_i} F| \arrow[r, "\simeq"] \arrow[d, "\otimes_i \phi (U_i)"', "\simeq"] & \int_{\sqcup_i U_i} F| \arrow[d, "\phi (\sqcup_i U_i)", "\simeq"']\\
            \otimes_i F (U_i) \arrow[r, "\simeq"] & F (\sqcup_i U_i),
        \end{tikzcd}
    \end{equation}
    %
    for each collection of disjoint open sets $\{U_i\}$. This, however, is guaranteed by the equivalences
    %
    \begin{equation}
        \disk[r]_{/\sqcup_i U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_i \disk[r]_{/U_i}.
    \end{equation}
    %
    Indeed, the fact that (sifted) colimits commute with the monoidal product on $\catC$ means that, for example in the case of two objects
    %
    \begin{align}
        \mathsf{colim}(K \xrightarrow{F} \catC) \otimes \mathsf{colim}(K' \xrightarrow{F'} \catC) &\simeq \mathsf{colim}(K \xrightarrow{F(-) \otimes \mathsf{colim}(K' \xrightarrow{F'} \catC)} \catC)\notag\\
        &\simeq \mathsf{colim}(K \xrightarrow{\mathsf{colim}(K' \xrightarrow{F(-) \otimes F'(-)} \catC)} \catC)\notag\\
        &\simeq \mathsf{colim}(K \times K' \xrightarrow{F \times F'} \catC \times \catC \xrightarrow{- \otimes -} \catC),
    \end{align}
    %
    for any (sifted) indexing $\infty$-categories $K, K'$.

@@

@@

In the opposite direction, we do not, in general, have a pullback functor. \cite{cg2016} provide a construction of a pullback in the case of open immersions, but we will only focus on the case of restrictions. Namely, given an open subset $U \subset X$ of a topological space $X$, and given a factorization algebra $F \in \falg_X$ we can clearly define a factorization algebra $F|_{U} \in \falg_U$ by restricting to those open subsets that are fully contained in $U$. Furthermore, this clearly holds not only for factorization algebras, but prefactorization algebras and locally constant factorization algebras too.

@@

\begin{proposition}\label{prop:exp_of_products_lc}
    Let $M$ and $N$ be stratified manifolds. The functor $\bar{\pi}$ descends to locally constant factorization algebras, and moreover, it is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
    \end{equation}
\end{proposition}

\begin{remark}
    The above proposition also appears as \cite[prop.18]{ginot2015}. The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$. Using \Cref{thm:disk_alg=lcfa}, the statement is implied by the fact that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
    \end{equation}
    %
    with the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}.
\end{remark}

@@

    One way to show the equivalence is to use factorization homology, as in \Cref{thm:disk_alg=lcfa}, to write a locally constant factorization algebra as $\int_{-} A \in \lcfa_{X \times Y} (\catC)$. Then using the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).} for factorization homology we get essential surjectivity because there are equivalences
    %
    \begin{equation}
        \int_{U \times V} A \xrightarrow{\ \ \simeq \ \ } \int_U \int_V \bar{\pi} A
    \end{equation}
    %
    between objects of $\catC$. As argued in the proof of \Cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables, which means that they rise to equivalences at the level of locally constant factorization algebras. In fact, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor. By \Cref{rem:fin_equiv_natural} this means that the equivalences are actually natural in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
\end{proof}

@@

\begin{proof}
    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is a weak equivalence of $\infty$-operads between $\disk (\mathsf{D}_n^*)$ and $\mathbb{E}_n$, i.e.
    %
    \begin{equation}
        \alg{\disk (\mathsf{D}_n^*)} \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n}.
    \end{equation}
    %
    But this is just the fact that the $\disk_{\mathsf{D}_n^*}$ $\infty$-operad gives rise to $\mathbb{E}_n$-algebras from \cref{prop:framed_ndisk=En}.
\end{proof}

@@

We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{prop:exp_of_products_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:

\begin{proposition}\label{prop:dunn_additivity}
    There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)). 
    \end{equation}
\end{proposition}

\begin{remark}
    The proof of \Cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are independent. 
\end{remark}

>>>>

\begin{remark}\label{rem:unpack_pfac_def}
    Let's unwind the above definition to understand the underlying data needed to define a prefactorization algebra. On the level of objects, for every open set $U$ we need to assign an object $F(U) \in \catC$. On the level of morphisms, given a pairwise disjoint set of opens $\{U_i\}_{i \in I}$ and an open $U$, such that the $U_i$ all lie in $U$ we need to assign a morphism in $\catC$
    %
    \begin{equation}
        \bigotimes_{i \in I} F(U_i) \xrightarrow{F(\{U_i\},U)} F(U).
    \end{equation}
    %
    As the notation suggests and the operadic symmetry condition guarantees, the maps $F(\{U_i\},U)$ only depend on the set of $U_i$ and not on any particular order of the $U_i$, which is also allowed on the left-hand side by the symmetric monoidal structure of $\catC$. Furthermore, the operadic associativity condition imposes that given pairwise disjoint $\{U_i\}_{i \in I}$ that all lie in $U$, and for each $i \in I$, pairwise disjoint $\{ V_{i, j}\}_{j \in J_i}$ that all lie in $U_i$, there is a commutative diagram in $\catC$
    %
    \begin{equation}
        \begin{tikzcd}
            \bigotimes\limits_{(i,j)} F(V_{i,j}) \arrow[rd, shorten <=-2ex, "\bigotimes\limits_{i} F(\{V_{i, j}\} {,} U_i)"'] \arrow[rr, "F( \{V_{i, j}\} {,} U)"] &   & F(U) \\
            & \bigotimes\limits_{i} F(U_i) \arrow[ru, "F( \{U_i \} {,} U)"'] &,          
        \end{tikzcd}
    \end{equation}
    %
    where the $(i,j)$ tensor product runs over all possible pairs $i \in I$ and $j \in J_i$. Finally, the operadic unitarity condition actually tells us that the morphisms $F(\{U\}, U)$ are equivalent to the identity morphism.

@@

    Given a Weiss cover $\mathscr{U}$ on $N$ we can restrict it to a Weiss cover $\mathscr{U}_{[B]}$ of $N_{[B]}$ by intersecting. The statement of \Cref{lem:weiss_to_ordinary} is that we can build an ordinary cover $\mathscr{U}_{i_{[B]},[B]}$ of $\mathrm{UConf}_{i_{[B]}}(N_{[B]})$. $\mathscr{V}_{\iota}^{[B]}$ is a cover if for any $p \in \widetilde{\mathsf{Fib}_{\iota}^{[B]}}(N)$ we can find an open $\widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U)$ that contains it. But this is indeed the case, because looking at the target $t(p)$ of the path $p$, we get $t(p) \in \mathrm{UConf}_{i_{[B]}}(N_{[B]})$, and we know that there exists a $U \in \mathscr{U}$ such that $\mathrm{UConf}_{i_{[B]}}(U_{[B]})$ covers $t(p)$ and subsequently also that $\widetilde{\mathsf{Fib}_{\iota}^{[B]}}(U)$ covers $p$.
\end{proof}

@@

\begin{proof}[Proof of {\Cref{thm:disk_alg=lcfa}}]
    To show essential surjectivity of $\int$, for each $F \in \lcfa_M (\catC)$ we will find an equivalence $\int F| \simeq F$ in $\lcfa_M (\catC)$, with $F|$ to be defined later. Since $\lcfa_M (\catC) \xrightarrow{} \alg{\opens(M)}$ is fully faithful, this amounts to finding an equivalence of prefactorization algebras, namely a family of equivalences
    %
    \begin{equation}
        \int_U F| \xrightarrow[\simeq]{\ \ \phi (U) \ \ } F(U),
    \end{equation}
    %
    one for each $(U \xhookrightarrow{} M) \in \mfld[r]_{/M}$, which are natural in $U$ and preserve the multiplicative structure (see \Cref{rem:unpack_pfac_def,cd:fa_morphisms}). Since $F$ is a locally constant factorization algebra the functor
    %
    \begin{equation}
        \lcfa_M (\catC) \xrightarrow{} \csheaves[W, lc](\mfld[r]_{/M}, \catC) \simeq \csheaves[W](\mfld_{/M}, \catC) \xrightarrow{} \mathsf{Fun}(\mfld_{/M}, \catC),
    \end{equation}
    %
    which we omit in the notation, allows us to consider $F$ as a functor from $\mfld_{/M}$. Furthermore, since $\disk[r]_{/U}$ is a Weiss sieve we can write
    %
    \begin{align}
        F(U) &\simeq \mathsf{colim} (\disk[r]_{/U} \xrightarrow{} \disk[r]_{/M} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{F} \catC).
    \end{align}
    %
    By consulting the commutative diagram
    % 
    \begin{equation}
        \begin{tikzcd}
            \disk[r]_{/U} \arrow[d] \arrow[r] & \disk_{/U} \arrow[d] & \\
            \disk[r]_{/M} \arrow[d] \arrow[r] & \disk_{/M} \arrow[d] \arrow[r, "F|"] & \catC, \\
            \mfld[r]_{/M} \arrow[r] & \mfld_{/M} \arrow[ru, "F"'] &  
        \end{tikzcd}
    \end{equation}
    %
    where $F|$ is the restriction of $F$ to disks, and using the fact that $\disk[r]_{/U} \xrightarrow{} \disk_{/U}$ is final (\cite[prop.2.22]{aft_fhstrat}) immediately gives us that
    %
    \begin{equation}
        F(U) \simeq \mathsf{colim} (\disk_{/U} \xrightarrow{} \disk_{/M} \xrightarrow{F|} \catC) \simeq \int_U F|.
    \end{equation}
    %
    Naturality of these equivalences is immediate from the construction because, as already used, each inclusion of open subsets $V \xhookrightarrow{} U$ gives a full subcategory inclusion $\disk[r]_{/V} \xhookrightarrow{} \disk[r]_{/U}$. Given this fact, to preserve the multiplicative structure it is enough to show that the following is a commutative diagram
    %
    \begin{equation}\label{eq:mult_strut_comm_square}
        \begin{tikzcd}
            \otimes_i \int_{U_i} F| \arrow[r, "\simeq"] \arrow[d, "\otimes_i \phi (U_i)"', "\simeq"] & \int_{\sqcup_i U_i} F| \arrow[d, "\phi (\sqcup_i U_i)", "\simeq"']\\
            \otimes_i F (U_i) \arrow[r, "\simeq"] & F (\sqcup_i U_i),
        \end{tikzcd}
    \end{equation}
    %
    for each collection of disjoint open sets $\{U_i\}$. This, however, is guaranteed by the equivalences
    %
    \begin{equation}
        \disk[r]_{/\sqcup_i U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_i \disk[r]_{/U_i}.
    \end{equation}
    %
    Indeed, the fact that (sifted) colimits commute with the monoidal product on $\catC$ means that, for example in the case of two objects
    %
    \begin{align}
        \mathsf{colim}(K \xrightarrow{F} \catC) \otimes \mathsf{colim}(K' \xrightarrow{F'} \catC) &\simeq \mathsf{colim}(K \xrightarrow{F(-) \otimes \mathsf{colim}(K' \xrightarrow{F'} \catC)} \catC)\notag\\
        &\simeq \mathsf{colim}(K \xrightarrow{\mathsf{colim}(K' \xrightarrow{F(-) \otimes F'(-)} \catC)} \catC)\notag\\
        &\simeq \mathsf{colim}(K \times K' \xrightarrow{F \times F'} \catC \times \catC \xrightarrow{- \otimes -} \catC),
    \end{align}
    %
    for any (sifted) indexing $\infty$-categories $K, K'$.

@@

In the opposite direction, we do not, in general, have a pullback functor. \cite{cg2016} provide a construction of a pullback in the case of open immersions, but we will only focus on the case of restrictions. Namely, given an open subset $U \subset X$ of a topological space $X$, and given a factorization algebra $F \in \falg_X$ we can clearly define a factorization algebra $F|_{U} \in \falg_U$ by restricting to those open subsets that are fully contained in $U$. Furthermore, this clearly holds not only for factorization algebras, but prefactorization algebras and locally constant factorization algebras too. As an interesting sidenote regarding stratifications, though, we note the following lemma.

@@

@@

\begin{proposition}[Additivity]\label{prop:exp_of_products_lc}
    Let $M$ and $N$ be stratified manifolds. The functor $\bar{\pi}$ descends to locally constant factorization algebras, and moreover, it is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
    \end{equation}
\end{proposition}

\begin{remark}
    The above proposition also appears as \cite[prop.18]{ginot2015}. The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$. Using \Cref{thm:disk_alg=lcfa}, the statement is implied by the fact that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \ \ \ } \disk_{/M \times N},
    \end{equation}
    %
    with $\otimes$ the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}.
\end{remark}

@@

    One way to show the equivalence is to use factorization homology, as in \Cref{thm:disk_alg=lcfa}. In this language, first we have to provide, for each locally constant factorization algebra in two variables $\int_{-}(\int_{-} A) \in \lcfa_{X}(\lcfa_{Y}(\catC))$, a locally constant factorization algebra $\int_{-} \bar{A} \in \lcfa_{X \times Y} (\catC)$ and an equivalence
    %
    \begin{equation}
        \bar{\pi} \int_{-} \bar{A} \xrightarrow[\simeq]{\ \ \phi \ \ } \int_{-} \big( \int_{-} A \big).
    \end{equation}
    %
    This is an equivalence in $\lcfa_{X}(\lcfa_{Y}(\catC))$, which means that it is a family of equivalences $\phi(U,V)$ in $\catC$
    %
    \begin{equation}
        \int_{U \times V} \bar{A} \xrightarrow[\simeq]{\ \ \phi (U,V)\ \ } \int_{U} \big( \int_{V} A \big),
    \end{equation}
    %
    one for each open $U \subset X$, and each open $V \subset Y$. Furthermore, this family is natural in $U$ and $V$ separately, and it is also multiplicative in $U$ and $V$ separately (cf. \Cref{rem:unpack_pfac_def}). Such a family of equivalences is provided by the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear from the context that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold (see \Cref{rem:fh_is_pushingforward}).} for factorization homology, which pointwise gives us the equivalences $\phi(U,V)$. As argued in the proof of \Cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables by the very functoriality of factorization homology, and they also preserve the multiplicative structure dues to the equivalences
    %
    \begin{equation}
        \disk[r]_{\sqcup_{i} U_i} \xrightarrow{\ \ \simeq \ \ } \bigtimes_{i} \disk[r]_{U_i},
    \end{equation}
    %
    together with the colimit preserving property of the monoidal product of $\catC$. This makes $\phi$ a fully-fledged equivalence of locally constant factorization algebras, which means that $\bar{pi}$ is essentially surjective. Moreover, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor. By \Cref{rem:fin_equiv_natural} this means that the equivalences are actually natural (or rather functorial) in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
\end{proof}

\begin{example}
    We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{prop:exp_of_products_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:

    \begin{proposition}\label{prop:dunn_additivity}
        There is an equivalence of $\infty$-categories
        %
        \begin{equation}
            \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)).
        \end{equation}
    \end{proposition}
\end{example}

\begin{remark}
    The proof of \Cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented above and the one in \cite{lurie_ha} are both independent of this special case. 
\end{remark}

@@

\begin{proof}
    With our setup, thanks to \Cref{thm:disk_alg=lcfa} and \Cref{lem:disk/M_to_disk}, it is sufficient to show that there is a weak equivalence of $\infty$-operads between $\disk (\mathsf{D}_n^*)$ and $\mathbb{E}_n$, i.e.
    %
    \begin{equation}
        \alg{\disk (\mathsf{D}_n^*)} \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n}.
    \end{equation}
    %
    But this is just the fact that the $\disk_{\mathsf{D}_n^*}$ $\infty$-operad gives rise to $\mathbb{E}_n$-algebras from \Cref{prop:framed_ndisk=En}.
\end{proof}

@@
